\documentclass{article}


\input{setup/final-report}
\input{setup/author}

\title{Predicting Stock Market with Bayesian Neural Network}


\begin{document}

\maketitle


\begin{abstract}
The randomness of stock market challenge investments to be reliable. Many of approaches has been introduced to find the hidden pattern behind the transitions. However, error estimation with non-parametric method is in the early stage. In this project, we used Bayesian neural network to predict discrete  time-series data with moving window of kernel. The Monte Carlo Markov Chain method is applied to measure the posterior distribution. The purpose is to provide a model-free approach with uncertainty quantification that is essential to the investment strategy. 
\end{abstract}

\section{Introduction}

\section{Methods}



\section{Dataset}

\paragraph{The dataset} contains the closing price per day for 4 stocks in 4 countries (Table \ref{tab:my_label}). These discrete time-series data is processed by normalization ($x_{i}' = \frac{x_{i} - x_{\min}}{x_{\max} - x_{\min}}$). The dataset is labeled by two timeframes: before and during COVID-19. Suppose the closing stock price is $[x_1, \dots, x_N]$ where $N$ is the length of the time series, the purpose is to predict the time series after the first few days of COVID-19 spreading.



The original data set is $x_t = \{x_{1}, ..., x_{Total}\}$, the training input is a matrix with dimension $m \times s$ (where m is the capture window, and $s$ is the number of samples). The sample is produced by shifting the original time series with lag of $2$.  These discrete time-series data is processed by normalization ($x_{i}' = \frac{x_{i} - x_{\min}}{x_{\max} - x_{\min}}$). 

\begin{equation}
\bar{x}_t = 
\underbrace{\begin{bmatrix}
    x_{1+(t-1)T} & \cdots & x_{m+(t-1)T}\\
    x_{3+(t-1)T} & \cdots & x_{2m+3+(t-1)T}\\
    \vdots & \vdots & \vdots 
\end{bmatrix}}_{\text{m(Capture windows)}}
\end{equation}

\begin{equation}
y_t = 
\underbrace{\begin{bmatrix}
    x_{m+(t-1)T + 1} & \cdots & x_{m+(t-1)T+ n}\\
    x_{2m+3+(t-1)T + 1} & \cdots & x_{2m+3+(t-1)T+ n}\\
    \vdots & \vdots & \vdots
\end{bmatrix}}_{\text{n (Prediction Horizons)}}
\end{equation}





\section{Submission of papers to NeurIPS 2022}


Please read the instructions below carefully and follow them faithfully.


\subsection{Style}

\end{document}